A large-scale analysis of racial disparities in police stops across the United

### 2019-12-11 lib/paper_results.Rmd
Add counts for mj tt panels
Update CI computation

Stop rates:
```{r stop_rates}
pfs$rates$stop %>%
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_annual_stop_rate = mean(annual_stop_rate),
    n = n()
  ) %>%
  kable()
```

@@

```{r search_rates}
tbl <- pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_n = mean(n),
    average_n_searches = mean(n_searches),
    average_search_rate = mean(search_rate),
    std_error = sqrt(
      average_search_rate * (1 - average_search_rate) / average_n
    ),
    CI_radius = 1.96 * std_error,
    CI_lower = average_search_rate - CI_radius,
    CI_upper = average_search_rate + CI_radius
  ) %>%
  ungroup()
tbl %>% kable()
ptbl <- tbl %>%
  mutate(
    n_success = average_n_searches,
    n_failure = average_n - average_n_searches
  )
pstate <- filter(ptbl, str_detect(agency, 'state'))
pcity <- filter(ptbl, str_detect(agency, 'municipal'))
```

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
tbl <- rbind(
  disp$city$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "cities",
      std_error = sqrt(average_hit_rate * (1 - average_hit_rate) / average_n_search_conducted),
      lower_CI = average_hit_rate - 1.96 * std_error,
      upper_CI = average_hit_rate + 1.96 * std_error,
    ),
  disp$state$outcome$results$aggregate_average_hit_rates %>% 
    mutate(
      geography = "states",
      std_error = sqrt(average_hit_rate * (1 - average_hit_rate) / average_n_search_conducted),
      lower_CI = average_hit_rate - 1.96 * std_error,
      upper_CI = average_hit_rate + 1.96 * std_error
    )
  ) %>% 
  select(geography, everything())
tbl %>% kable()
ptbl <- tbl %>%
  mutate(
    n_success = average_n_contraband_found,
    n_failure = average_n_search_conducted - average_n_contraband_found
  )
pstate <- filter(ptbl, geography == "states")
pcity <- filter(ptbl, geography == "cities")
```

@@

>>>>

Stop rates:
```{r stop_rates}
pfs$rates$stop %>%
  mutate(
    agency = if_else(city == "Statewide", "state patrol", "municipal pd"),
    var = annual_stop_rate * (1 - annual_stop_rate) / population
  ) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    stop_rate = mean(annual_stop_rate),
    std_error = sqrt(sum(var)) / n(),
    lower_ci = stop_rate - 1.96 * std_error,
    upper_ci = stop_rate + 1.96 * std_error
  ) %>%
  kable()
```

@@

```{r search_rates}
tbl <- pfs$rates$search %>% 
  mutate(
    agency = if_else(city == "Statewide", "state patrol", "municipal pd"),
    var = search_rate * (1 - search_rate) / n
  ) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_search_rate = mean(search_rate),
    std_error = sqrt(sum(var)) / n(),
    lower_ci = average_search_rate - 1.96 * std_error,
    upper_ci = average_search_rate + 1.96 * std_error
  ) %>%
  ungroup()
tbl %>% kable()
# TODO(danj): Make sure these make sense given new CI computations
ptbl <- tbl %>%
  mutate(
    n_success = average_n_searches,
    n_failure = average_n - average_n_searches
  )
pstate <- filter(ptbl, str_detect(agency, 'state'))
pcity <- filter(ptbl, str_detect(agency, 'municipal'))
```

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
tbl <- rbind(
  disp$city$outcome$results$hit_rates %>% 
    group_by(geography, subject_race) %>% 
    summarize(
      hit_rate = weighted.mean(`contraband_found where search_conducted`, n_search_conducted),
      var = hit_rate * (1 - hit_rate) / sum(n_search_conducted)
    ) %>% 
    group_by(subject_race) %>% 
    summarize(
      geography = "cities",
      hit_rate = mean(hit_rate),
      std_error = sqrt(sum(var)) / n(),
      lower_ci = hit_rate - 1.96 * std_error,
      upper_ci = hit_rate + 1.96 * std_error
    ),
  disp$state$outcome$results$hit_rates %>% 
    group_by(geography, subject_race) %>% 
    summarize(
      hit_rate = weighted.mean(`contraband_found where search_conducted`, n_search_conducted),
      var = hit_rate * (1 - hit_rate) / sum(n_search_conducted)
    ) %>% 
    group_by(subject_race) %>% 
    summarize(
      geography = "states",
      hit_rate = mean(hit_rate),
      std_error = sqrt(sum(var)) / n(),
      lower_ci = hit_rate - 1.96 * std_error,
      upper_ci = hit_rate + 1.96 * std_error
    )
  ) %>% 
  select(geography, everything())
tbl %>% kable()
# TODO(danj): Make sure these make sense given new CI computations
ptbl <- tbl %>%
  mutate(
    n_success = average_n_contraband_found,
    n_failure = average_n_search_conducted - average_n_contraband_found
  )
pstate <- filter(ptbl, geography == "states")
pcity <- filter(ptbl, geography == "cities")
```

@@

Number of points in CO panel: `r comma_num(mj$plots$counts$co)`

Number of points in WA panel: `r comma_num(mj$plots$counts$wa)`
